\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/experiment.tex
Exp to QR code payment

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}\shuqing{Photos.}
	\label{fig:PBS_products}
\end{figure}

@@

Whiling providing convenience to users, it brings security issues. 
We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank. 
A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
	\caption{Bar/QR code payment procedure}
	\label{fig:qr_payment_procedure}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}\shuqing{Photos that we took.}
	\label{fig:PBS_products}
\end{figure}

@@

Though it provides convenience to users, it also brings security issues. 
We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices to them. 
The attackers are able to modify their rented power banks, return it to a power bank station as normal.
Then the subsequent users will unknowingly connect to such malicious power banks, which endangers the financial security and data security of users.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
	\caption{Bar/QR code payment procedure}
	\label{fig:qr_payment_procedure}
\end{figure}
